### 2022-03-15 manuscript.tex
Update 03.p53.md [ci skip]
This build is based on
https://github.com/scherzerthesis/thesis/commit/d1ac79b39eca2a98ddaf51e9083282c9a05eaed3.

This commit was created by the following CI build and job:
https://github.com/scherzerthesis/thesis/commit/d1ac79b39eca2a98ddaf51e9083282c9a05eaed3/checks
https://github.com/scherzerthesis/thesis/actions/runs/1989118837

This manuscript
(\href{https://scherzerthesis.github.io/thesis/v/9213662b7adaf086956a4d1fa83ad98751f19610/}{permalink})
was automatically generated
from \href{https://github.com/scherzerthesis/thesis/tree/9213662b7adaf086956a4d1fa83ad98751f19610}{scherzerthesis/thesis@9213662}
on March 15, 2022.

@@

\begin{figure}
\hypertarget{fig:14}{%
\centering
\includegraphics{images/p53_5.png}
\caption{\textbf{Mutant-p53 expression cells have distinct transcriptome compared to p53-null cells.} \textbf{(A)} Volcano plot of differentially-expressed genes. \textbf{(B)} Upregulated pathways using GSEA with Hallmark gene sets.}\label{fig:14}
}
\end{figure}

\begin{figure}
\hypertarget{fig:14}{%
\centering
\includegraphics{images/p53_6.png}
\caption{\textbf{Mutant-p53 expression cells have distinct transcriptome compared to p53-null cells.} \textbf{(A)} Volcano plot of differentially-expressed genes. \textbf{(B)} Upregulated pathways using GSEA with Hallmark gene sets.}\label{fig:14}
}
\end{figure}

\begin{figure}
\hypertarget{fig:14}{%
\centering
\includegraphics{images/p53_7.png}
\caption{\textbf{Mutant-p53 expression cells have distinct transcriptome compared to p53-null cells.} \textbf{(A)} Volcano plot of differentially-expressed genes. \textbf{(B)} Upregulated pathways using GSEA with Hallmark gene sets.}\label{fig:14}
}
\end{figure}

\begin{figure}
\hypertarget{fig:14}{%
\centering
\includegraphics{images/p53_8.png}
\caption{\textbf{Mutant-p53 expression cells have distinct transcriptome compared to p53-null cells.} \textbf{(A)} Volcano plot of differentially-expressed genes. \textbf{(B)} Upregulated pathways using GSEA with Hallmark gene sets.}\label{fig:14}
}
\end{figure}

>>>>

This manuscript
(\href{https://scherzerthesis.github.io/thesis/v/d1ac79b39eca2a98ddaf51e9083282c9a05eaed3/}{permalink})
was automatically generated
from \href{https://github.com/scherzerthesis/thesis/tree/d1ac79b39eca2a98ddaf51e9083282c9a05eaed3}{scherzerthesis/thesis@d1ac79b}
on March 15, 2022.

@@

\begin{figure}
\hypertarget{fig:14}{%
\centering
\includegraphics{images/p53_4.png}
\caption{\textbf{Mutant-p53 expression cells have distinct transcriptome compared to p53-null cells.} \textbf{(A)} Volcano plot of differentially-expressed genes. \textbf{(B)} Upregulated pathways using GSEA with Hallmark gene sets.}\label{fig:14}
}
\end{figure}

\begin{figure}
\hypertarget{fig:14}{%
\centering
\includegraphics{images/p53_4.png}
\caption{\textbf{Mutant-p53 expression cells have distinct transcriptome compared to p53-null cells.} \textbf{(A)} Volcano plot of differentially-expressed genes. \textbf{(B)} Upregulated pathways using GSEA with Hallmark gene sets.}\label{fig:14}
}
\end{figure}
